### 2015-03-18 evaluation.tex
draft table
updates to table

Granularities: Full-force; Coarse; MemoryRegion

>>>>

Granularities: Yield-All (\corral without \whoop); \yieldcoarse; \yieldmr

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table*}[t]
\small
\centering
\begin{tabular}{l rrr rr rr rr rr}
\centering
\input{experiments/tables/granularity.tex}
\end{tabular}
\caption{Results ...}
\label{tab:granularity}
\end{table*}

The machzwd watchdog driver explodes when running on vanilla \corral, because in some entry point pairs it attempts to analyse a large number of memory regions. For example for the entry point pair write vs init, it instruments interleavings at 26 different memory regions in a single invocation of \corral, which required approximately 1000 seconds to analyse. The same entry point pair is found race-free by \whoop. Using this information in \corral with the \yieldmr instrumentation, the pair takes less than a second to analyse. The \yieldcoarse instrumentation does not perform as well, because it works in the binary granularity of racy or non-racy entry points.
